### 2013-04-10 MSteenhagen-CV.tex
Fixed wishful thinking about start date PhD
Work exp
Fixed caps and typo in Work experience

\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)

\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}

\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}

@@

\marginhead{{\vskip 0.9em}Service to the \newline Profession}
\medskip

@@

\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.

\ind 2010--Present. Co-Organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.

\ind 2009--Present. Research Assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.

\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.

@@

\ind 2008. Chair of the organisation for \emph{The Philosopher's Rally,} an international graduate conference in Philosophy, Utrecht.

>>>>

\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)

\ind 2011. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}

\ind 2011. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}

@@

\marginhead{{\vskip 0.9em}Work experience}
\medskip

@@

\ind 2012--Present. Website editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.

\ind 2010--Present. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.

\ind 2009--Present. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.

\ind 2012. Assistant organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.

@@

\ind 2008. Chair of the organisation for \emph{The Philosophers' Rally,} an international graduate conference in Philosophy, Utrecht.
